Hypotheses

### 2019-10-10 analysis/output/figures/hypotheses/Hypotheses.Rmd
Working on more plots but keep running into errors

```{r plot-marginals, echo = FALSE}
# Specify the covariate.
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 1                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
    draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    filter(
    # levels ==   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
      covariates ==  "Income: Less than $10,000 to $300,000 or more") %>% 
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

>>>>

```{r plot-marginals, echo = FALSE}
# Specify the covariate.
intercept <- 0                            # Intercept-only
public_affairs <- 1                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
    draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    filter(
    # levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
      covariates ==  "Liberal to Conservative") %>% 
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 4)
}
```

Error: Faceting variables must have at least one value
